---
title: "4_LER_spad"
author: "Lucile regouby"
date: "21/11/2022"
output:
  html_document:
    df_print: paged
  pdf_document: default
  word_document: default
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

## Contexte sur l'analyse 

We want to answer to this theme of our project weed regulation and competition in the cover, Assing this question : Which species work better in association as a cover crop? 

## Importation of data an libraries

### Libraires importation

```{r cars}
library(tidyverse)
library(ggplot2)
library(agricolae)
library(report)
```

### data importation 

```{r}
LER.1= read.table("4_LER.csv", header = TRUE,sep = ";", dec = ",")
line_content = read.table("Line_content.csv", header = TRUE, sep = ";", dec = ",")

line_content%>%
  mutate(Line=as.factor(Line))-> line_content

LER<- LER.1%>%
  mutate(Line = as.factor(Line))%>%
  full_join(line_content)

write.csv(LER, "LER_table_mean.csv")

```


## 1.  -- LER Analysis -- The mixed cover will be more productive in biomass than the monoculture cover.

### Complete LER analysis between all the treatments 

graph of the values of LER in function of the treatment
```{r}
LER %>%
  filter( mono_mix == "mix") %>%
  filter (Specie != "Weed") %>%
  group_by(cover_crop)%>%
  summarise(mymean=mean(LER_cc, na.rm=T),
            mysd=sd(LER_cc, na.rm=T))%>%
  mutate(ymax=mymean+mysd, ymin=mymean-mysd) %>%
  ggplot (aes(x = reorder(cover_crop, mymean), y = mymean,
              ymin=ymin, ymax=ymax, na.rm=T)) + 
  geom_point()+
  geom_errorbar()+
  theme(axis.text.x = element_text(angle=45))+
  geom_hline(yintercept=1, linetype="dashed", color = "red")+
  labs(x="Cover crop mix", y="LER value", title = "LER value in function of the mix")

```
choisir celui là parce que le boxplot on ne voit pas bien les petits points 


Graph en boxplot ==> ne va pas le mettre 

```{r}
view(LER)

LER %>%
  filter( mono_mix == "mix")%>%
  filter (Specie != "Weed") %>%
  group_by(Line)%>%
  #summarise(mymean=mean(LER_cc, na.rm=T))%>%
  ggplot ()+
  aes(x = reorder(Line, LER_cc), y=LER_cc, fill=Line)+
  geom_boxplot()+
  labs(x="Number of treatment", y="LER value", title = "LER value in function of the treatment")
  
```
n'arrive pas à reorder, il faudrait enlever des valeurs parce que qu'elles ne permettent pas de bien voir la répartition des autres

vérification des hypothèses de l'anova :

```{r}
shapiro.test(LER$LER_cc)

```
shapiro test pvalue<0,05 ==> no normality of LER_cc

kruskal wallis test 
```{r}
kruskal.LER.cc <- kruskal(LER$LER_cc, LER$Line,  console = T)
```
no significantive difference 



### Analysis of the LERp for each specie between mix and monoculture -- NOT USEFUL AS SAID AURELIE

#### Table with LER, LERP 
un tableau sur libre office 


## Spad analysis ##############

### importation of the data and pivot : 
```{r}
spad = read.table("4_bis_spad.csv", header = TRUE,sep = ",", dec = ".")

spad%>%
  mutate(Line = as.factor(Line), nature=as.factor(nature),
         legumes=as.factor(legumes), Date=as.factor(Date)) -> spad
spad%>%
  full_join(line_content) -> spad

```

### spad analysis for both dates

#### For all the treatments and all the dates 

verification that we can use anova 
```{r}
shapiro.test(spad$spad_value)
```
pvalue < 0,05 ==> not normality of the values ==> can't use anova 

test de kruskal:

```{r}
kruskal.spad.all <- kruskal(spad$spad_value, spad$Line, console = T)
```

graph with the letters of the kruskal

useless because it is not whant we want to show but code is usefull
```{r}
posthock.spad.all <- kruskal.spad.all$groups %>% 
  rownames_to_column("Line") %>% 
  select(Line, groups)%>%
  mutate(Line= as.factor(Line))

spad$Line<-with(spad, reorder(Line, spad_value, median, na.rm=T))



view(spad)

#c'est pas du tout ça qu'on veut 

spad%>%
  filter(Line!=1)%>%
  group_by(cover_crop)%>%
  full_join(posthock.spad.all)%>%
  ggplot () +
  aes(x = cover_crop, y = spad_value, label = groups, fill=Line)+
  geom_text(aes(y=0))+
  geom_boxplot()+
  theme(axis.text.x = element_text(angle=45), legend.position='none')+
  labs(x="Species in the treatment", y="Spad values for the specie", title = "Spad values from 17/10/2022 and 07/11/2022 in function of the species in the treatment")
```

Il est possible de faire la même chose pour les espèces séparément entre les monoculture et les mixes 
#### For barley 

preparing the data

```{r}
spad.b <- spad %>%
  filter(Specie=="Barley")

```

test to know if we can do the anova
```{r}
shapiro.test(spad.b$spad_value)
```
not normality of the variables ==> can't do the anova

kruskal test:

```{r}
kruskal.spad.b <- kruskal(spad.b$spad_value, spad.b$Line, console = T)

```

graph to show this
```{r}
posthock.spad.b <- kruskal.spad.b$groups %>% 
  rownames_to_column("Line") %>% 
  select(Line, groups)%>%
  mutate(Line= as.factor(Line))


spad.b%>%
  group_by(cover_crop)%>%
  full_join(posthock.spad.b)%>%
  ggplot () +
  aes(x = reorder(cover_crop, spad_value ,na.rm = TRUE), y = spad_value, label = groups, fill=Line)+
  geom_text(aes(y=-1))+
  geom_boxplot()+
  theme(axis.text.x = element_text(angle=45), legend.position='none')+
  labs(x="Treatments containing barley", y="Spad values for barley", title = "Spad values for barley in function of the treatment containing barley ")
```

#### For mustard

preparing the data 
```{r}
spad.m <- spad %>%
  filter(Specie=="Mustard")
```

test to know if we can do an anova 
```{r}
shapiro.test(spad.m$spad_value)

```
no normality of values ==> no anova 

kruskal test
```{r}
kruskal.spad.m <- kruskal(spad.m$spad_value, spad.m$Line, console = T)

```

graph:
```{r}
posthock.spad.m <- kruskal.spad.m$groups %>% 
  rownames_to_column("Line") %>% 
  select(Line, groups)%>%
  mutate(Line= as.factor(Line))


spad.m%>%
  group_by(cover_crop)%>%
  full_join(posthock.spad.m)%>%
  ggplot () +
  aes(x = reorder(cover_crop, spad_value ,na.rm = TRUE), y = spad_value, label = groups, fill=Line)+
  geom_text(aes(y=17.5))+
  geom_boxplot()+
  theme(axis.text.x = element_text(angle=45), legend.position='none')+
  labs(x="Treatments containing mustard", y="Spad values for mustard", title = "Spad values for mustard in function of the treatment containing mustard ")
```


#### Radish

preparing the data
```{r}
spad.r <- spad %>%
  filter(Specie=="Radish")
```

test to know if we can do an anova 
```{r}
shapiro.test(spad.r$spad_value)

```
normality of the spad values

for the homogeneity of variances
```{r}
leveneTest(spad_value~Line, data=spad.r)
```
homogeity of the variances 
==> can use an anova :

```{r}
anova.spad.r<- lm(spad_value~cover_crop, spad.r)
anova(anova.spad.r)
summary(anova.spad.r)
```

test posthoc
```{r}
tukey.spad.r <- HSD.test(anova.spad.r, "cover_crop", alpha = 0.05, group=TRUE, main = NULL, console=FALSE)
print(tukey.spad.r)

posthock.spad.r <- tukey.spad.r$groups %>% 
  rownames_to_column("cover_crop") %>% 
  select(cover_crop, groups)

view(posthock.spad.r)
```

graph:

```{r}
spad.r%>%
  group_by(cover_crop)%>%
  full_join(posthock.spad.r)%>%
  ggplot () +
  aes(x = reorder(cover_crop, spad_value ,na.rm = TRUE), y = spad_value, label = groups, fill=cover_crop)+
  geom_text(aes(y=17.5))+
  geom_boxplot()+
  theme(axis.text.x = element_text(angle=45), legend.position='none')+
  labs(x="Treatments containing radish", y="Spad values for radish", title = "Spad values for radish in function of the treatment containing radish ")


```

#### For Faba bean

preparing the data set 
```{r}
spad.fb <- spad %>%
  filter(Specie=="Faba bean")

```

test if we can do an anova :
```{r}
shapiro.test(spad.fb$spad_value)
```
not normality of spad values 

kruskal test
```{r}
kruskal.spad.fb <- kruskal(spad.fb$spad_value, spad.fb$Line, console = T)
```
not significative difference between the treatments ==> do we have to do a plot? Yess I think so 

graph
```{r}
posthock.spad.fb <- kruskal.spad.fb$groups %>% 
  rownames_to_column("Line") %>% 
  select(Line, groups)%>%
  mutate(Line= as.factor(Line))


spad.fb%>%
  group_by(Line)%>%
  full_join(posthock.spad.fb)%>%
  ggplot () +
  aes(x = reorder(cover_crop, spad_value ,na.rm = TRUE), y = spad_value, label = groups, fill=Line)+
  geom_text(aes(y=30))+
  geom_boxplot()+
  theme(axis.text.x = element_text(angle=45), legend.position='none')+
  labs(x="Treatments containing Faba bean", y="Spad values for faba bean", title = "Spad values for faba bean in function of the treatment containing faba bean ")
```




#### Fenugreek
prepapring the data set 
```{r}
spad.fn <- spad %>%
  filter(Specie=="Fenugreek")
```

test if we can do an anova 
```{r}
kruskal.spad.fn <- kruskal(spad.fn$spad_value, spad.fn$Line, console = T)
```
not significative difference : do we have to do a plot ?

graph:
```{r}
posthock.spad.fn <- kruskal.spad.fn$groups %>% 
  rownames_to_column("Line") %>% 
  select(Line, groups)%>%
  mutate(Line= as.factor(Line))


spad.fn%>%
  group_by(Line)%>%
  full_join(posthock.spad.fn)%>%
  ggplot () +
  aes(x = reorder(cover_crop, spad_value ,na.rm = TRUE), y = spad_value, label = groups, fill=Line)+
  geom_text(aes(y=30))+
  geom_boxplot()+
  theme(axis.text.x = element_text(angle=45), legend.position='none')+
  labs(x="Treatments containing fenugreek", y="Spad values for fenugreek", title = "Spad values for fenugreek in function of the treatment containing fenugreek ")
```



### spad analysis for the first date - NOT interesting as we have it for all the dates 

#### For all the treatments 
```{r}
spad.1 <- spad%>%
  filter( Date == "17/10")
```


test anova

```{r}
anova.spad.all.1 <-lm(spad_value~Line+zone,spad.1)
anova(anova.spad.all.1)
summary(anova.spad.all.1)
```
anova significative !!!!

vérification des hypothèses de l'anova: 

```{r}
par(mfrow = c(2,2))
plot(anova.spad.all)
```
hypothèse de normalité pas incroyable ==> est ce qu'on peut vraiment faire une anova?

test de kruskal:

```{r}
kruskal.spad.all <- kruskal(spad.1$spad_value, spad.1$Line, console = T)
```

graph with the letters of the kruskal

```{r}
posthock.spad.all <- kruskal.spad.all$groups %>% 
  rownames_to_column("Line") %>% 
  select(Line, groups)%>%
  mutate(Line= as.integer(Line))
spad.1%>%
  group_by(Line)%>%
  summarise(mymean=mean(spad_value, na.rm=T),
            mysd=sd(spad_value, na.rm=T))%>%
  mutate(ymax=mymean+mysd, ymin=mymean-mysd) %>%
  full_join(posthock.spad.all)%>%
  ggplot (aes(x = reorder(Line, mymean), y = mymean, label = groups, 
              ymin=ymin, ymax=ymax, na.rm=T)) + 
  geom_point()+
  geom_text(aes(y=85))+
  geom_errorbar()+
  labs(x="Line", y="spad value", title = "Sapad value in function of the treatment")
```

tukey because anova is great ??

```{r}
# tukey.spad.all.1 <- HSD.test(spad.1, "Line", alpha=0.05, group=TRUE, main = NULL, console = FALSE)
# print(tukey.spad.all.1)
# posthock.spad.all.2 <- tukey.spad.all.1%>%
#   rownames_to_column("Line")%>%
#   select(Line, groups)
# 
# view(posthock.spad.all.2)



### Spad analysis for the second date -- j'ai mis les deux dates dans la première analyse 
je ne vait pas le faire c'est juste un copier coller 

```{r}
spad.2 <- spad%>%
  filter( Date == "07/11")

```


test anova

```{r}
anova.spad.all.2 <-lm(spad_value~Line,spad.2)
anova(anova.spad.all.2)
```
anova significative 

vérification des hypothèses :

```{r}
par(mfrow = c(2,2))
plot(anova.spad.all)
```
la normalité est pas dingue 

test de kruskal:
```{r}
kruskal.spad.all.2 <- kruskal(spad.2$spad_value, spad.2$Line, console = T)

```

graph with letters of the kruskal

```{r}
posthock.spad.all.2 <- kruskal.spad.all.2$groups %>% 
  rownames_to_column("Line") %>% 
  select(Line, groups)%>%
  mutate(Line= as.integer(Line))

spad.2%>%
  group_by(Line)%>%
  summarise(mymean=mean(spad_value, na.rm=T),
            mysd=sd(spad_value, na.rm=T))%>%
  mutate(ymax=mymean+mysd, ymin=mymean-mysd) %>%
  full_join(posthock.spad.all.2)%>%
  ggplot (aes(x = reorder(Line, mymean), y = mymean, label = groups, 
              ymin=ymin, ymax=ymax, na.rm=T)) + 
  geom_point()+
  geom_text(aes(y=65))+
  geom_errorbar()+
  labs(x="Line", y="spad value", title = "Sapad value of 07/11 in function of the treatment")
```




### Spad analysis of the impact of the legume and the mix or monoculture effect
```{r}
spad%>%
  group_by(Line)%>%
  ggplot (aes(x = nature, y = legumes, na.rm=T)) + 
  geom_jitter()+
  labs(x="Nature of the treatment", y="Presence of legume in the treatment", title = "Distributions of spad values between the nature of the treatment and the presence or not of legumes in the treatment")
```
same repartition between mix and monoculture and with or without legumes in the treatment ==> I don't know how to analyse it 

test statistique 

```{r}
anova.spad.legumes.mix <-lm(spad$spad_value~spad$nature+spad$legumes+spad$nature*spad$legumes, spad)
anova(anova.spad.legumes.mix)
```

The spad values are mostly explained by the interaction between the nature of the cover and the presence of legumes.



```{r pressure, echo=FALSE}

```

Note that the `echo = FALSE` parameter was added to the code chunk to prevent printing of the R code that generated the plot.
